---
title: "Mint Data Processing"
author: "GaryFH"
date: "February 8, 2018"
output: md_document
editor_options: 
  chunk_output_type: console
---




###Setup environment

```{r, message=FALSE,warning=FALSE}
suppressWarnings(library(dplyr))

```


###Look at income and try to reconcile - note that $5,000 of interest income was cashed and not part of Mint income.

```{r, message=FALSE,warning=FALSE}


d1<-tbl_df(read.csv("transactions03062019.csv"))
d1$Date<- as.Date(d1$Date,format="%m/%d/%Y")
d1<-filter(d1,Date>=as.Date("2018-01-01")&Date<=as.Date("2018-12-31"))

d2<-filter(d1,Transaction.Type=="credit")

d222<-filter(d2,Category=="appraisal income")
print(paste("Total Interest Income = ","$",sum(d222$Amount),sep=""))

d223<-filter(d2,Category=="Interest Income")
print(paste("Total Interest Income = ","$",(sum(d223$Amount)+5000),sep=""))

d2b<-group_by(d2,Category)
print(summarise(d2b,sum(Amount)),n=nrow(d2b))
print(summarise(group_by(d2,Description),sum(Amount)),n=nrow(d2))
#View(filter(d2b,Category=="Interest Income"))
#View(filter(d2b,Category=="appraisal income"))
#View(filter(d2b,Category=="Reimbursement"))
#View(filter(d2b,Description=="Thank You"))

```


###Overview of all Categories

```{r, message=FALSE,warning=FALSE}
d11<-group_by(d1,Category)
print(summarise(d11,sum(Amount)),n=nrow(d11))


```


###Total Health Insurance - subtracted $2,000 from below to adjust for non insurance expenses

```{r, message=FALSE,warning=FALSE}
d4<-filter(d1,Category=="Health Insurance")
d4<-select(d4,Date,Description,Amount)
d44<-d4
d45<-mutate(d44,z="`")
d45<-select(d45,Date,Description,z,Amount)
d45$Amount<- sprintf("$ %7.2f", d45$Amount)
print(d45,n=nrow(d45))
print(paste("Total paid to Health Insurance = $",sum(d4$Amount),sep = ""))

```

###Health Savings Account

```{r, message=FALSE,warning=FALSE}
dd4<-filter(d1,Category=="HealthSavingsAccount")
dd4<-select(dd4,Date,Original.Description,Amount)
dd44<-dd4
dd45<-mutate(dd44,z="`")
dd45<-select(dd45,Date,Original.Description,z,Amount)
dd45$Amount<- sprintf("$ %7.2f", dd45$Amount)
print(dd45,n=nrow(dd45))
print(paste("Total paid to Health Savings Account = $",sum(dd4$Amount),sep = ""))

```


###Total Business Meals

```{r, message=FALSE,warning=FALSE}
d3<-filter(d1,Category=="Business Meals")
d3<-select(d3,Date,Original.Description,Amount)
d33<-d3
d33<-mutate(d33,z="`")
d33<-select(d33,Date,Original.Description,z,Amount)
d33$Amount<- sprintf("$ %7.2f", d33$Amount)
print(d33,n=nrow(d33))
print(paste("Total Business Meals = $",sum(d3$Amount),sep = ""))

```



###Business phone/internet

```{r, message=FALSE,warning=FALSE}

dd5<-filter(d1,Category=="bus phone/internet")
dd5<-select(dd5,Date,Original.Description,Amount)
dd55<-dd5
dd55<-mutate(dd55,z="`")
dd55<-select(dd55,Date,Original.Description,z,Amount)
dd55$Amount<- sprintf("$ %7.2f", dd55$Amount)
print(dd55,n=nrow(dd55))
print(paste("Total paid to Business Phone/Internet = $",sum(dd5$Amount),sep = ""))


```


###Business Travel

```{r, message=FALSE,warning=FALSE}

dd6<-filter(d1,Category=="Business Travel")
dd6<-select(dd6,Date,Original.Description,Amount)
dd66<-dd6
dd66<-mutate(dd66,z="`")
dd66<-select(dd66,Date,Original.Description,z,Amount)
dd66$Amount<- sprintf("$ %7.2f", dd66$Amount)
print(dd66,n=nrow(dd66))
print(paste("Total paid to Business Travel = $",sum(dd6$Amount),sep = ""))


```


###Office Supplies - note that $1350 of the total below was for liability insurance.

```{r, message=FALSE,warning=FALSE}

d8<-filter(d1,Category=="Office Supplies")
d8<-select(d8,Date,Original.Description,Amount)
d88<-d8
d88<-mutate(d88,z="`")
d88<-select(d88,Date,Original.Description,z,Amount)
d88$Amount<- sprintf("$ %7.2f", d88$Amount)
print(d88,n=nrow(d88))
print(paste("Total paid to Office Supplies = $",sum(d8$Amount),sep = ""))


```



###Charity

```{r, message=FALSE,warning=FALSE}

d6<-filter(d1,Category=="Charity")
d6<-select(d6,Date,Description,Amount)
d66<-d6
d66<-mutate(d66,z="`")
d66<-select(d66,Date,Description,z,Amount)
d66$Amount<- sprintf("$ %9.2f", d66$Amount)
print(d66,n=nrow(d66))
print(paste("Total paid to Charity = $",sum(d6$Amount),sep = ""))


```


###Doctor&Dentist

```{r, message=FALSE,warning=FALSE}

d7<-filter(d1,Category=="Doctor" | Category=="Dentist")
d7<-select(d7,Date,Category,Description,Amount)
d77<-d7
d77<-mutate(d77,z="`")
d77<-select(d77,Date,Category,Description,z,Amount)
d77$Amount<- sprintf("$ %7.2f", d77$Amount)
print(d77,n=nrow(d77))
print(paste("Total paid to Doctor and Dentist = $",sum(d7$Amount),sep = ""))


```



###Driver Cost

```{r, message=FALSE,warning=FALSE}

d8<-filter(d1,Category=="Driver cost")
d8<-select(d8,Date,Original.Description,Amount)
d88<-d8
d88<-mutate(d88,z="`")
d88<-select(d88,Date,Original.Description,z,Amount)
d88$Amount<- sprintf("$ %7.2f", d88$Amount)
print(d88,n=nrow(d88))
print(paste("Total paid to Driver costs = $",sum(d8$Amount),sep = ""))


```


###Estimated Federal & State tax payments

```{r, message=FALSE,warning=FALSE}

dd7<-filter(d1,Category=="Federal Tax" | Category=="State Tax")
dd7<-select(dd7,Date,Category,Original.Description,Amount,Notes)
dd77<-dd7
dd77<-mutate(dd77,z="`")
dd77<-select(dd77,Date,Category,Original.Description,z,Amount,Notes)
dd77$Amount<- sprintf("$ %7.2f", dd77$Amount)
print(dd77,n=nrow(dd77))



```

###Property and other taxes

```{r, message=FALSE,warning=FALSE}

d8<-filter(d1,Category=="Taxes")
d8<-select(d8,Date,Original.Description,Amount)
d88<-d8
d88<-mutate(d88,z="`")
d88<-select(d88,Date,Original.Description,z,Amount)
d88$Amount<- sprintf("$ %7.2f", d88$Amount)
print(d88,n=nrow(d88))
print(paste("Total paid to property&other TAXES = $",sum(d8$Amount),sep = ""))


```


###Business Services,Electronics & Software,Legal,Printing,Tuition

```{r, message=FALSE,warning=FALSE}

d7<-filter(d1,Category=="Business Services" | Category=="Electronics & Software"| Category=="Legal"| Category=="Printing"| Category==" Tuition")
d7<-select(d7,Date,Category,Description,Amount)
d77<-d7
d77<-mutate(d77,z="`")
d77<-select(d77,Date,Category,Description,Amount)
d77$Amount<- sprintf("$ %7.2f", d77$Amount)
print(d77,n=nrow(d77))
print(paste("Total paid to Various Business expenses = $",sum(d7$Amount),sep = ""))


```





```{r, message=FALSE,warning=FALSE}



```


